```{r Load Data}setwd("d:/workflow/_Stuff/Education/11_R/20170720_UDACITY COURSE/lesson3/")pf <- read.delim('pseudo_facebook.tsv')```### Third Qualitative Variable
```{r Third Qualitative Variable}ggplot(aes(x = gender, y = age),       data = subset(pf, !is.na(gender))) + geom_boxplot() +  stat_summary(fun.y = mean, geom = "point", shape = 4)
ggplot(aes(x = age, y = friend_count),       data = subset(pf, !is.na(gender))) +   geom_line(aes(color = gender), stat = 'summary', fun.y = mean)
```
# Write code to create a new data frame,# called 'pf.fc_by_age_gender', that contains# information on each age AND gender group.```{r Task 1}pf <- read.delim('pseudo_facebook.tsv')pf.fc_by_age_gender <- pf %>%  filter(!is.na(gender)) %>%  group_by(age, gender) %>%  summarise(mean_friend_count = mean(as.numeric(friend_count)),            median_friend_count = median(as.numeric(friend_count)),            n = n()) %>%  ungroup() %>%  arrange(age, gender)
head(pf.fc_by_age_gender)```
***
### Plotting Conditional SummariesNotes:
```{r Plotting Conditional Summaries}ggplot(aes(x = age, y = mean_friend_count),       data = pf.fc_by_age_gender) +   geom_line(aes(color = gender))```
***
### Ratio Plot# Plot the ratio of the female to male median# friend counts using the data frame# pf.fc_by_age_gender.wide.# Add a horizontal line to the plot with# a y intercept of 1, which will be the# base line. Use the parameter# linetype in geom_hline to make the# line dashed.
```{r Ratio Plot}library(reshape2)pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,                                  age ~ gender,                                  value.var = "median_friend_count")str(pf.fc_by_age_gender.wide)
ggplot(aes(x = age, y = female / male),       data = pf.fc_by_age_gender.wide) +   geom_line() +  geom_hline(yintercept = 1, alpha = 0.2, linetype = 2)```
***# Create a variable called year_joined# in the pf data frame using the variable# tenure and 2014 as the reference year.
### Third Quantitative Variable
```{r Third Quantitative Variable}pf$year_joined <- floor(2014 - pf$tenure/365)```
***
### Cut a Variable# Create a new variable in the data frame# called year_joined.bucket by using# the cut function on the variable year_joined.# You need to create the following buckets for the# new variable, year_joined.bucket#        (2004, 2009]#        (2009, 2011]#        (2011, 2012]#        (2012, 2014]
```{r Cut a Variable}pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))```
***
### Plotting it All Together# Create a line graph of friend_count vs. age# so that each year_joined.bucket is a line# tracking the median user friend_count across# age. This means you should have four different# lines on your plot.
```{r Plotting it All Together}table(pf$year_joined.bucket, useNA = 'ifany')
ggplot(aes(x = age, y = friend_count),       data = subset(pf, !is.na(year_joined.bucket))) +  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)```
***
### Plot the Grand MeanNotes:
```{r Plot the Grand Mean}ggplot(aes(x = age, y = friend_count),       data = subset(pf, !is.na(year_joined.bucket))) +  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +   geom_line(stat = 'summary', fun.y = mean, linetype = 2)```
***
### Friending RateNotes:
```{r Friending Rate}with(subset(pf, pf$tenure >= 1), summary(friend_count / tenure))```
***
### Friendships Initiated
# Create a line graph of mean of friendships_initiated per day (of tenure)# vs. tenure colored by year_joined.bucket.
```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),       data = subset(pf, pf$tenure >= 1)) +  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) ```
***
### Bias-Variance Tradeoff RevisitedNotes:
```{r Bias-Variance Tradeoff Revisited}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),       data = subset(pf, tenure >= 1)) +  geom_line(aes(color = year_joined.bucket),            stat = 'summary',            fun.y = mean)
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),       data = subset(pf, tenure > 0)) +  geom_line(aes(color = year_joined.bucket),            stat = "summary",            fun.y = mean)
ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),       data = subset(pf, tenure > 0)) +  geom_line(aes(color = year_joined.bucket),            stat = "summary",            fun.y = mean)
ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),       data = subset(pf, tenure > 0)) +  geom_line(aes(color = year_joined.bucket),            stat = "summary",            fun.y = mean)
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),       data = subset(pf, tenure > 0)) +  geom_smooth(aes(color = year_joined.bucket))```
***
### Histograms RevisitedNotes:
```{r Histograms Revisited}yo <- read.csv("yogurt.csv", header = TRUE, sep = ",")str(yo)ggplot(aes(x = price, color = I("black"), fill = I("blue")), data = yo) +  geom_histogram(binwidth = 10)
qplot(data = yo, x = price, fill = I("blue"), binwidth = 10)
```
***
### Number of Purchases# Create a new variable called all.purchases,# which gives the total counts of yogurt for# each observation or household.
```{r Number of Purchases}yo <- transform(yo, all.purchases = strawberry+blueberry+pina.colada+plain+mixed.berry)summary(yo$all.purchases)```
***
### Prices over Time# Create a scatterplot of price vs time.
# This will be an example of a time series plot.
```{r Prices over Time}ggplot(aes(x = time, y = price), data = yo) +  geom_jitter(alpha = 1/2, shape = 21, fill= "blue")```
***
### Looking at Samples of Households
```{r Looking at Sample of Households}set.seed(1947)sample.ids <- sample(yo$id, 16)
ggplot(aes(x = time, y = price),        data = subset(yo, id %in% sample.ids)) +  facet_wrap(~id) +  geom_line() +   geom_point(aes(size = all.purchases) , pch = 1)```
***
### Heat MapsNotes:
```{r}nci <- read.table("nci.tsv")colnames(nci) <- c(1:64)```
```{r}nci.long.samp <- melt(as.matrix(nci[1:200,]))names(nci.long.samp) <- c("gene", "case", "value")head(nci.long.samp)
ggplot(aes(y = gene, x = case, fill = value),  data = nci.long.samp) +  geom_tile() +  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))```
